Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex
changing the image of added lines
algunos retoques mas

The first algorithm to identifying bug-introducing code changes automatically was proposed by Sliwerski et al.~\cite{sliwerski2005changes}. Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version. The SZZ algorithm uses the CVS \texttt{annotate} command\footnote{Other versioning systems provide similar functionality to CVS \texttt{annotate}; for instance, git offers \texttt{blame}.} to identify the last commit that touched these lines.

An improvement to the SZZ algorithm is described by Kim et al.~\cite{kim2006automatic}. There the authors used annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion. Also, they avoid some false positives by not considering blank spaces, changes in the format or changes in the comments.

Sinha et al. present another technique to identify the origins of a bug in~\cite{sinha2010buginnings}. Their technique is not text-based technique, as the SZZ algorithm, the authors analyze the effects of bug-fix changes on program dependencies. So, taking into account the semantics of the source code they achieved higher accuracy in identifying the origins of a bug.

@@

Williams et al. revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}. Yang et al. applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}.
Finally, some bug prediction algorithms are based on SZZ; Kim et al. showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}. \grex{Creo que deberiamos hablar de mas papers que hacen uso de SZZ y derivados}.

The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community. Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 463 times as of January 
2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations.

The SZZ algorithm (and its \emph{successors}) have been widely used in the research community.
Williams et al. revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}. Yang et al. applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes
Finally, some bug prediction algorithms are based on SZZ; Kim et al. showed how to classify file changes as buggy or clean using change information features and sour code terms~\cite{kim2008classifying}.

In the research literature, we can already find methods that consider other sources of information than the previous commit. In fact, German et al.~\cite{german2009change} 
point out that software is in constant change, and that changes performed may have impact across the whole system and may lead to the manifestation of bugs in unchanged parts. In this case, a bug emerges in a different location from the source of the bug, which is a change to a function somewhere else in the source code base. \grex{Quizas mirar si hay mas articulos en esta linea. No es muy importante esto.}

@@

All data needed to analyze when the bug was introduced can be obtained from the issue tracking systems and the code review systems used generally by free/open source software (FOSS) projects. In our analysis, we have focused on Launchpad\footnote{\url{https://launchpad.net/}} as issue tracking system, and Gerrit\footnote{\url{https://www.gerritcodereview.com/}} as code review supporting tool, as they are widely used by FOSS projects nowadays, but our methodology should be generalizable to any such tool.

@@

We classify a total of 459 tickets using the tool, resulting in 917 reviews. Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits. This process requires manual inspection by researchers. In the mean classifying a ticket takes between 5 and 10 minutes per ticket, although the amount of time decreases with experience as could be expected.

\gema{[...] se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?} \grex{No es muy importante, pero quedaria bien}

@@

\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
\begin{figure}[ht]
\centering
\includegraphics[height=2.5cm]{manyprevious.png}
\caption{Previous commits (right): \textit{e7be0a988} (line 218) and \textit{e5296c1da} (line 2422).}
\label{fig:manyprevious}       % Give a unique label
\end{figure}

@@

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases or due to our limited knowleadge about the code. The figure \ref{fig:add} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines. In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\grex{Gema, puedes poner un ejemplo de estas dos cosas? Uno de solo added lines y otro de limited knowledge. Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
\begin{figure}[ht]
\centering
\includegraphics[height=1cm]{addedlines.png}
\label{fig:added}       % Give a unique label
\caption{Example of added lines where we are unable to decide which previous commit caused the bug}
%52919
\end{figure}

@@

There are other cases where it is difficult to determine if the change is the cause. For instance, when additional conditions are added to \emph{if}s or \emph{else}s, one might think that in the previous commit those were not included due to an error, so that the previous commit becomes the cause of the bug. However, situations exist where the additional conditions in an if appear because of the introduction of a new functionality, and thus the line in the previous commit was correct at the time it was introduced. In our analysis, if the latter situation is not explicity mentioned we have considered that the previous commit caused the error.

@@

%The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
The number of the tickets extracted form Launchpad is relatively high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry. It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult.

@@

\nocite{*}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}

>>>>

Bug-introducing code changes has been a \emph{hot} topic in the mining software repositories research community for over a decade. The most used algorithm to identify bug-introducing code changes automatically was proposed by Sliwerski et al.~\cite{sliwerski2005changes}, which is an improvement to previous approaches~\cite{vcubranic2003hipikat,fischer2003analyzing,fischer2003populating}. Currently, it is a well-known algorithm called SZZ, which is based on text differences to discover modified, added and deleted lines between the bug-fix and its previous version. The SZZ algorithm uses the CVS \texttt{annotate} command\footnote{Other versioning systems provide similar functionality to CVS \texttt{annotate}; for instance, git offers \texttt{blame}.} to identify the last commit that touched these lines.

There are several research articles that propose improvements to the SZZ algorithm. Kim et al.~\cite{kim2006automatic} use annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion. Also, they avoid some false positives by not considering blank spaces, changes in the format or changes in the comments. Williams et al. revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.

The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community. Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 463 times as of January 
2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations. Hence, there is a myriad of articles that propose its use for a large number of uses. For instance, Yang et al. applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}. Kim et al. showed how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}. Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}. Izquierdo et al. use the SZZ algorithm to see if developers are fixing their own bugs~\cite{izquierdo2011developers}. Yin et al. use it to find out how many fixes to bugs introduce new bugs~\cite{yin2011fixes}. Fejzer et al. us it to support code review~\cite{fejzer2015supporting}. Asaduzzaman et al. apply the SZZ algorithm on Android to study maintenance implications~\cite{asaduzzaman2012bug}.

%Bachmann et al. on the missing link between comments in change logs and bug fixes ~\cite{bachmann2010missing}
%Wu et al. propose a tool solution~\cite{wu2011relink}

The question of whether a bug report is really a bug or not has been widely studied in the 
mining software repositories research literature in the last years. So, Pan et al. classify the different types of bug-fix patterns that most commonly exist~\cite{pan2009toward}. Antoniol et al. have use a text-based approach to classify bug reports into corrective maintenance and other kinds of activities~\cite{antoniol2008bug}. Herzig et al. have done a manual examination of thousands of bug reports and have found that around a third of them are misclassified, in the sens that they were not a bug report but a feature request, internal refactoring or update to documentation~\cite{herzig2013s}. They show that almost 40\% of the files marked as defective did not have a bug, and suggest that this missclassification introduces bias in bug prediction models and tools.

Prechelt and Pepper offer a good overview of what they call defect-insertion circumstance analysis. They point out that one of the obstacles in the way of a reliable analysis are the ``additional changes between defect insertion time and defect correction time that happen to happen at subsequently defect-corrected locations''~\cite{prechelt2014software}. Some methods that consider sources of information other than the previous commit already exist. So, German et al.~\cite{german2009change} 
point out that software is in constant change, and that changes performed may have impact across the whole system and may lead to the manifestation of bugs in unchanged parts. In this case, a bug emerges in a different location from the source of the bug, which is a change to a function somewhere else in the source code base.

Sinha et al. present another technique to identify the origins of a bug in~\cite{sinha2010buginnings}. Their technique is not text-based technique, as the SZZ algorithm, as the authors analyze the effects of bug-fix changes on program dependencies. So, taking into account the semantics of the source code they achieved higher accuracy in identifying the origins of a bug.

@@

%\grex{Quizas mirar si hay mas articulos en esta linea. No es muy importante esto.}

@@

All data needed to analyze when the bug was introduced can be obtained from the issue tracking systems and the code review systems used generally by free/open source software (FOSS) projects. In our analysis, we have focused on Launchpad\footnote{\url{https://launchpad.net/}} as issue tracking system, and Gerrit\footnote{\url{https://www.gerritcodereview.com/}} as code review supporting tool, as they are widely used by FOSS projects nowadays, but our methodology should be adaptable to any such tool.

@@

We classify a total of 459 tickets using the tool, resulting in 917 reviews\footnote{One review was discarded as it was left empty.}. Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits. This process requires manual inspection by researchers. In the mean classifying a ticket takes between 5 and 10 minutes per ticket, although the amount of time decreases with experience as could be expected.

%\gema{[...] se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?} \grex{No es muy importante, pero quedaria bien}

@@

\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}

\begin{figure}[ht]
\centering
\includegraphics[height=2.5cm]{manyprevious.png}
\caption{Previous commits (right): \textit{e7be0a988} (line 218) and \textit{e5296c1da} (line 2422).}
\label{fig:manyprevious}       % Give a unique label
\end{figure}

@@

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not being the cause. We were unable to decide in 42 cases or due to our limited knowledge about the code. Figure~\ref{fig:added} shows an example of fix bug commit where only lines have been added. In such a case, we are not able to know which previous commit is the one that caused the error, so we classify it as \textit{Undecided}. %\grex{Gema, puedes poner un ejemplo de estas dos cosas? Uno de solo added lines y otro de limited knowledge. Si el ejemplo es verdadero, mejor.}
\gema{Me falters el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
In addition, we discarded 40 more previous commits because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.

\begin{figure}[ht]
\centering
\includegraphics[height=2.5cm]{addedlines.png}
\label{fig:added}       % Give a unique label
\caption{Example of scenario where the bug fix is composed only of lines added. The fix bug commit with lines added in green can be seen on the left (subfigure (1)), and the file as it was before the fix bug commit on the right (subfigure (2)).}
%52919
\end{figure}

@@

There are other cases where it is difficult to determine if the change is the cause. For instance, when additional conditions are added to \emph{if}s or \emph{else}s, one might think that in the previous commit those were not included due to an error, so that the previous commit becomes the cause of the bug. However, situations exist where the additional conditions in an if appear because of the introduction of a new functionality, and thus the line in the previous commit was correct at the time it was introduced. In our analysis, if the latter situation is not explicitly mentioned we have considered that the previous commit caused the error.

@@

%The limited sample size of tickets used in this research is the major threat to its validity. %It may happen, that only with 100 seemingly random tickets, there may be a prior unknown tendency. This is in fact similar to~\cite{sliwerski2005changes}, where the trend indicates that most bugs are fixed on Fridays.
The number of the tickets extracted form Launchpad is relatively high, but probably not as high as to state that it can be representative of all free/open source systems, or the software industry. It has not to be forgotten that the analysis requires a lot of human effort, so that achieving large numbers of cases is difficult. However, it should be noted that the amount of tickets in in the order of magnitude of similar studies found in the research literature, for instance Hindle's et al. article on large commits, where 100~\cite{hindle2008large}.

@@

%\nocite{*}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}
